\documentclass[12pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[margin=0.25in]{geometry}
\author{Javier Pimentel}
\begin{document}	
	My Phase 3 is almost complete, it is able to send and receive icmp message. It sends a initial icmp message, udp train, and several following icmp messages. When it a echo reply is received the time is recorded and after they all arrive the RTT is displayed on the screen. I was not able to read from /dev/random and used urandom instead. \\
	
	I opted to use threads instead of fork() because it made it easier to pass variable between functions. Also because threads are initiated faster and require less resources. \\
	
	If I could do the program again I would of used a different method of storing the time stamps.\\
	
Challenges:
\begin{itemize}
	\item Sending icmp / udp messages on the same socket
	\item Race condition between threads
	\item Reading from the /dev/random file
\end{itemize}

To resolve the first issue I looked at other examples of programs that send udp packets I found that they used a different protocol when opening the socket. After trying IPPROTO RAW I was able to send and receive messages on the same socket.This caused a problem later on because I used the same protocol to open the receiving socket, there where no issues after changing it to IPPRO ICMP.

In order to record a time stamp for each message I used a global array so that each function could access it. Since they where running on different threads it created a race condition. The first thread would write the sending time and it would get overridden by the second. I was getting negative RTT vales. To fix the problem I used pthread mutex so that it could only be access by a single thread at a time. 

On my system the time it took to read from /dev/random was inconsistent, at time it would take minutes. In order to avoid the long delay I used urandom instead, since its nonblocking.

\end{document}